\bf Model Visualization Techniques for a Social Network Model

### 2017-04-10 paper.Rnw
add some references and citations of layout algorithms.

Some layout algorithms were designed to mimic physical systems, drawing the graphs based on the "forces" connecting them. The network's edges act as springs pushing and pulling the nodes in 2D space. Others use properties of the network's adjaceny matrix in order to place the nodes. Some commonly used layout algorithms are  XX ADD MORE DETAIL LATER XX
\begin{itemize}
\item Kamada-Kawai
\item Fructerman-Reingold
\item Multi-dimensional scaling
\item Eigen
\end{itemize}

@@

>>>>

Some layout algorithms were designed to mimic physical systems, drawing the graphs based on the "forces" connecting them. The network's edges act as springs pushing and pulling the nodes in 2D space. Others use properties of the network's adjaceny matrix in order to place the nodes. Some commonly used layout algorithms are  
\begin{itemize}
\item Kamada-Kawai: The ``graph theoretic distance'' from one node to another is represented in the 2D node placement. This network drawing method results in several nice properties such as ``symmetric drawings [and] a relatively small number of edge crossings'' \citep[p. 15]{kamadakawai}.
\item Fructerman-Reingold: This algorithm is a spring-embedder type where ``the vertices behave as [...] celestial bodies, exerting attractive and repulsive forces on one another,'' where the simple goal of drawing connected nodes near to each other \citep[p. 1131]{fruchterman-reingold}.
\item Multi-dimensional scaling:
\item Eigen
\end{itemize}

@@

<<histogramalters, fig.width = 8, fig.height=11, fig.cap="Probabilities of">>=
ansnullchains %>% group_by(period, rep) %>% 
  mutate(ms = row_number()) %>% 
  filter(ms == 1, period == 1) %>% 
  mutate(alterProb = exp(logAlterProb),
         ego = as.numeric(as.character(ego)),
         alter = as.numeric(as.character(alter))) %>% 
  ungroup() %>% 
  group_by(ego, alter) %>% 
  summarize(count = n(), alterProb = unique(alterProb)) %>% ungroup() %>% 
  group_by(ego) %>% 
  mutate(csum = cumsum(alterProb)) %>% 
  arrange(ego, csum) -> cumprobs 
cumprobs$ego <- factor(paste0("V",cumprobs$ego+1), levels = paste0("V", 1:16))

cumprobs %>% ggplot() + geom_histogram(aes(x = alter, weight = alterProb), color = 'black', fill = 'white', binwidth = 1) + scale_x_continuous(labels = paste0("V",1:16), breaks = 0:15) + coord_flip() + facet_wrap(~ego, labeller = "label_both") + theme_gray()

# cprobslist <- split(cumprobs, cumprobs$ego)
# plots <- list()
# for(i in 1:length(cprobslist)){
#   cprobslist[[i]] %>%
#   ggplot() + 
#   geom_histogram(aes(x = as.numeric(as.character(alter)),
#                      y = alterProb), stat = 'identity', fill = 'white', color = 'black') + 
#   geom_line(aes(x = as.numeric(as.character(alter)), 
#                 y = csum)) + 
#   geom_point(aes(x = as.numeric(as.character(alter)), 
#                 y = csum)) +
#   scale_x_continuous(limits = c(-.5, 15), breaks = 0:15, labels = 0:15) +   
#   geom_hline(yintercept = 1, color = 'red', linetype = 'dashed') + 
#   labs(x = "alter", y = expression(p[ij]), title = paste("Ego node:", names(cprobslist)[i])) + # ylab(expression(p[ij])) + 
#   theme_gray() + 
#     theme(plot.title = element_text(size = 10), 
#           axis.title = element_text(size = 8), 
#           plot.margin = unit(rep(0,4),"pt")) -> p
#   plots[[i]] <- p
# }
# grid.arrange(plots[[1]], plots[[2]], plots[[3]], plots[[4]],
#              plots[[5]], plots[[6]], plots[[7]], plots[[8]],
#              #plots[[9]], plots[[10]], plots[[11]], plots[[12]],
#              #plots[[13]], plots[[14]], plots[[15]], plots[[16]], 
#              ncol = 2, padding = unit(0, 'line'))
@
